Uncertainty propagation in neural networks for sparse coding

### 2018-03-10 paper/BayesianLISTA.tex
minor corrections

The probability of a zero $\omega^*$ equals to the probability mass of the original distribution from the interval $[-\lambda, \lambda]$
\begin{align}
\begin{split}
\omega^* &= \mathbb{P}(x^*=0) = \mathbb{P}(x \in [-\lambda, \lambda]) \\
&= \Phi\left(\frac{\lambda-m}{\sqrt{v}}\right) - \Phi\left(\frac{-\lambda-m}{\sqrt{v}}\right). 
\end{split}
\end{align}
where $\Phi(\cdot)$ is the standard Gaussian cumulative distribution function.

@@

Figure \ref{fig:z_new_testing} demonstrates the comparison of the sampled distribution and approximated distribution for lemma \ref{thm:soft_thresholding}. For sampled distribution, $10000$ values are sampled from the Gaussian vector and propagated through soft thresholding, then one of the dimensionalities is plotted. The approximated distribution is computed according to lemma \ref{thm:soft_thresholding}.
\begin{figure}[t]
\includegraphics[width=\columnwidth]{d_testing}
\caption{Approximation of product of Gaussians.}
\label{fig:d_testing}
\end{figure}

\begin{figure}[t]
\includegraphics[width=\columnwidth]{z_new_testing}
\caption{Approximation of propagation through soft thresholding}
\label{fig:z_new_testing}
\end{figure}

@@

Figure~\ref{fig:unsersampling_synthetic} gives the results of predictive performance for different observation sizes $K$. The number of layers is set as $L=4$. In the previous experiment both Bayesian and classical \textsc{lista} shows similar results with this number of layers. The results of Figure~\ref{fig:unsersampling_synthetic} confirms this competitive behaviour between two \textsc{lista} networks. Baselines show similar results in terms of F measure and underperform in terms of \textsc{nmse}.

The experiments on synthetic data demonstrate that Bayesian \textsc{lista} provides competitive results in terms of predictive accuracy while additionally estimating uncertainty of predictions.

@@

Figures \ref{fig:mnist_100} and \ref{fig:mnist_250} present quality on the validation set with dictionaries of size $100$ and $250$.  The experiment with $K=100$ presents ``severe'' conditions for the algorithms: the very limited size of the training dataset combined with the small dimensionality of observations. The Baysian \textsc{lista} is able to learn even under these conditions, significantly outperforming \textsc{lista} that demonstrate very poor results. Under easier condition of the second experiment with $K=250$ both \textsc{lista} networks converge to the similar results. However, the Bayesian \textsc{lista} demonstrates remarkably better convergence rate. Both baselines are unable to learn in these experiments.

>>>>

The probability of a zero $\omega^*$ equals to the probability mass of the original distribution from the interval $[-\lambda, \lambda]$
\begin{align}
\begin{split}
\omega^* &=\operatorname{P}(x^*=0) = \operatorname{P}(x \in [-\lambda, \lambda]) \\
&= \Phi\left(\frac{\lambda-m}{\sqrt{v}}\right) - \Phi\left(\frac{-\lambda-m}{\sqrt{v}}\right). 
\end{split}
\end{align}
where $\Phi(\cdot)$ is the standard Gaussian cumulative distribution function.

@@

Figure \ref{fig:z_new_testing} demonstrates the comparison of the sampled distribution and approximated distribution for lemma \ref{thm:soft_thresholding}. For sampled distribution, $10000$ values are sampled from the Gaussian vector and propagated through soft thresholding, then one of the dimensionalities is plotted. The approximated distribution is computed according to lemma \ref{thm:soft_thresholding}.

%\subfloat[\textsc{nmse} on validation]{\includegraphics[width=0.5\columnwidth]{graphics/mnist/100_non_normalised_nmse_valid}}

%\begin{figure}[t]
%\includegraphics[width=\columnwidth]{d_testing}
%\caption{Approximation of product of Gaussians.}
%\label{fig:d_testing}
%\end{figure}
%
%\begin{figure}[t]
%\includegraphics[width=\columnwidth]{z_new_testing}
%\caption{Approximation of propagation through soft thresholding}
%\label{fig:z_new_testing}
%\end{figure}

\begin{figure}[t]
\subfloat[Approximation of the \newline product of Gaussians]{\includegraphics[width=0.5\columnwidth]{d_testing}}
%\label{fig:d_testing}
\subfloat[Approximation of the propagation through soft thresholding]{\includegraphics[width=0.5\columnwidth]{z_new_testing}}
%\caption{Approximation of propagation through soft thresholding}
%\label{fig:z_new_testing}
\end{figure}

@@

Figure~\ref{fig:unsersampling_synthetic} gives the results of predictive performance for different observation sizes $K$. The number of layers is set as $L=4$. In the previous experiment Bayesian and classical \textsc{lista} show similar results with this number of layers. The results of Figure~\ref{fig:unsersampling_synthetic} confirms this competitive behaviour between two \textsc{lista} networks. Baselines show similar results in terms of F measure and underperform in terms of \textsc{nmse}.

Overall, the experiments on synthetic data demonstrate that Bayesian \textsc{lista} provides competitive results in terms of predictive accuracy.

@@

Figures \ref{fig:mnist_100} and \ref{fig:mnist_250} present quality on the validation set with dictionaries of size $100$ and $250$.  The experiment with $K=100$ presents severe conditions for the algorithms: the very limited size of the training dataset combined with the small dimensionality of observations. The Bayesian \textsc{lista} is able to learn under these conditions, outperforming \textsc{lista} that demonstrates poor results. Under better conditions of the second experiment with $K=250$ both \textsc{lista} networks converge to the similar results. However, the Bayesian \textsc{lista} demonstrates remarkably better convergence rate. Both baselines are unable to perform well in these experiments.
